% ============================================================================
%  SNIPPETS FOR INSERTION INTO THE MAIN PAPER
%  Instructions: find the anchor text below and append the snippet after it.
% ============================================================================

% ---- INSERTION 1 -----------------------------------------------------------
% Location: Section 5.5 (Ecological regression), end of the endogeneity paragraph.
% Anchor: "...move $\hat{\gamma}$ further from the fraud hypothesis."
% Insert AFTER that sentence, as a new paragraph:
% ============================================================================

Appendix~\ref{app:swing} extends this analysis to the mesa level.
Matching each polling station across both rounds yields a panel of
$79{,}672$ mesas, of which 1,004 are contested.
The mean swing from Peru Libre's first-round share to Castillo's
second-round share is $+31.3$~pp---exactly what binary consolidation
of anti-Fujimori votes predicts mechanically.
Contested mesas exhibit a mean swing of $+29.3$~pp, \emph{lower} than
the $+31.3$~pp uncontested average (Welch $t = -6.0$,
$p = 2.6 \times 10^{-9}$).
The mesa-level OLS residual is $-0.020$ for contested mesas,
confirming that the fraud hypothesis---which requires a positive residual
in precisely those mesas---is directly rejected.


% ---- INSERTION 2 -----------------------------------------------------------
% Location: Section 6.1 (Discussion -- Why fraud allegations gained traction),
%           end of the SECOND paragraph (the one about geographic anomalies).
% Anchor: "...near-unanimous results are not unusual and do not require manipulation."
% Insert AFTER that sentence, as a new paragraph:
% ============================================================================

The mesa-level swing analysis in Appendix~\ref{app:swing} bears directly
on this perception.
Of the 116 mesas recording a swing of $\geq 80$ percentage points
between rounds, only 2 are contested.
Lima and Amazonas account for 88\,\% of extreme-swing mesas---not the
southern highland departments of Puno, Ayacucho, or Cusco that anchored
the fraud allegations.
These extreme swings reflect high anti-Fujimori consolidation from former
Sagasti and Toledo voters who had near-zero Peru Libre support in the first
round, not manipulation: the mesas with the most striking two-round swings
were almost entirely unchallenged by Fujimori's own legal team.
